\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2013-09-06 paper.tex
Cleaning headers (remove unused packages)

%\documentclass[preprint,5p]{elsarticle}
\documentclass[final,3p,times]{elsarticle}

@@

\usepackage[english]{babel}
\usepackage{cite}
\usepackage{graphicx, subfigure}
\usepackage{url}
\graphicspath{{figs/}}
\DeclareGraphicsExtensions{.pdf,.jpg,.png}

@@

\usepackage{listings}
\usepackage{alltt}
\usepackage{fancyvrb}

%\usepackage[bookmarks]{hyperref}

\usepackage{booktabs}
%\usepackage{tabularx}

\newcommand{\concept}[1]{{\small \texttt{#1}}}

\newcommand{\stmt}[1]{{\footnotesize \tt $\langle$ #1\relax$\rangle$}}

@@

@@

Knowledge is represented as RDF triples in the OWL sub-language. Each
time triples are added or removed from the knowledge base, a Description
Logics reasoner ({\sc Pellet}\footnote{\url{http://clarkparsia.com/pellet/}})
classifies the whole ontology and inserts all possible inferred triples.

>>>>

%\documentclass[preprint,5p]{elsarticle}
\documentclass[preprint,3p,times]{elsarticle}

@@

\usepackage[english]{babel}
\usepackage{cite}
\usepackage{graphicx, subfigure}

@@

\newcommand{\concept}[1]{{\small \texttt{#1}}}
\newcommand{\stmt}[1]{{\footnotesize \tt $\langle$ #1\relax$\rangle$}}

@@

\graphicspath{{figs/}}
\DeclareGraphicsExtensions{.pdf,.jpg,.png}

@@

Knowledge is represented as RDF triples in the OWL sub-language. Each
time triples are added or removed from the knowledge base, a Description
Logics reasoner ({\sc Pellet}\footnote{\tt http://clarkparsia.com/pellet/})
classifies the whole ontology and inserts all possible inferred triples.
